### 2021-02-19 paper.tex
Kommentare Michelle

\subsection*{Motivation}%
Students of medical informatics need to internalize complex relations between large amounts of concepts of health information systems and their management~\cite{visualizationoflargeontologies}.
Graph-based Linked Data visualization~\cite{linkeddatavisualization} is well suited for this task but the available tools do not fit our requirements~\cite{visualizationoflargeontologies}.
%\cite{snikgraphposter}

@@

Users should see the structure of the whole graph at once, but also be able to start at a certain resource and explore its neighbourhood incrementally.

>>>>

\subsection*{Motivation}%
Students of medical informatics need to\todo{Vorschlag von Michelle: Dozenten können Ausschnitte des Graphen verwenden um in Vorlesungen den Zusammenhang von Konzepten vereinfacht darzustellen bzw. die Studenten diese Zusammenhänge durch Recherche im Graphen erarbeiten lassen. } internalize complex relations between large amounts of concepts of health information systems and their management~\cite{visualizationoflargeontologies}.
Graph-based Linked Data visualization~\cite{linkeddatavisualization} is well suited for this task but the available tools do not fit our requirements~\cite{visualizationoflargeontologies}.
%\cite{snikgraphposter}

@@

Users should see the structure of the whole graph at once, but also be able to start at a certain resource and explore its neighbourhood incrementally.
\todo{Vorschlag von Michelle: Verwendung in der Lehre setzt intuitive/leicht erlernbare Benutzung des Graphen voraus um zu vermeiden wertvolle Vorlesungszeit an ein Tutorial zu verlieren --> Bekannet Tastaturshortcuts, Drag&Drop, übersichtliches }
